---
title: "Introduction to StatComp20035"
author: "Yu Jiayi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp20035__ is a simple R package developed to introduce the statistical computing course homework and including two simple functions to practice the R packages .Two functions are considered, one is about using Monte Carlo method to estimate the value of complex integral, the second function is about Gibbs sampler applied to normal distribution

## Monte Carlo integral

The source R code  is as follows:
```{r,eval=FALSE}
integral <-function(a,b)
{
N <- 10000
z <- numeric(N)
u <- runif(N,0,1)
z <- (b-a)*u + a
f <- function(x) 
{
  exp(-x)/(1+x^2)
}
integral <- mean(f(z)/(b-a))
integral
}
}
```

## Gibbs sampler
The source R code  is as follows:
```{r,eval=FALSE}
gibbs<-function (n, r) 
{
   mat <- matrix(ncol = 2, nrow = n)
  x <- 0 
  y <- 0
   mat[1, ] <- c(x, y)
   for (i in 2:n) {
      x <- rnorm(1, r * y, sqrt(1 - r^2))
      y <- rnorm(1, r * x, sqrt(1 - r^2))
      mat[i, ] <- c(x, y)
   }
   mat
}
bvn <- gibbs(n,r)
plot(bvn,type="l")
```